%\linespread{1.5} \normalsize
\section{Conclusion}
This report has discussed the characteristics of hybrid plasmonic (HP) waveguides (HPWs) and their potential applications such as optical ring resonators and nanoantenna. The objectives of this project were to study the properties of various structures of HP-waveguides and to use those structures for different devices used in photonic integrated circuits. Both objectives were met. Three different structures of HP-waveguides were simulated and their characteristics were studied at optical communication wavelength of $\uplambda = \text{1550 nm}$. Adding further to that, an optical ring resonator notch filter based on hybrid dielectric-loaded plasmonic waveguide (HDLW) was simulated and its transmission characteristics were studied at both constructive and destructive interference wavelengths. A high extinction ratio of 22.5 dB and 24.9 dB is obtained at r = 2 $\upmu \text{m}$ and 5 $\upmu \text{m}$ respectively. While low transmission loss of 0.8 dB and 0.5 dB is obtained at radii 2 $\upmu \text{m}$ \& 5 $\upmu \text{m}$ respectively. We also investigated a horn-shaped nanoantenna based on HP-waveguide with silicon-on-insulator (SOI) configuration and its input HP-waveguide was simulated. All simulations were carried out using finite element method (FEM) in COMSOL Multiphysics software and graphs were plotted with the help of MATLAB.

\section{Future Work}
In future, we would like to investigate hybrid plasmonic waveguides of other potential applications such as biosensors and optical switches. Also, we would like to extend our work on optical ring resonators to simulate different kind of optical filters with better extinction ratio and low loss.